Target Markdown

### 2023-08-10 _targets.Rmd
Add a pre-draft

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"))
source(here::here("R", "network_metrics.R"))
source(here::here("R", "string_replacements.R"))
source(here::here("R", "stability_decomposition.R"))
source(here::here("R", "model_helpers.R"))
```

@@

```{r targets raw_sim}
list(
tar_target(sim_fw_file, here::here("data", "sim_fw"), format = "file"),
  tar_target(sim_fw, readRDS(sim_fw_file)),
  tar_target(sim_fw_df, as.data.frame(sim_fw)),
  tar_target(sim_fw_cons, readRDS(here::here("data", "sim_fw_cons"))),
  tar_target(sim_fw_cons_df, as.data.frame(sim_fw_cons))
  )
```

>>>>>>> Stashed changes

@@

```{targets sem-process}
list(
  tar_target(sem_model_list,
    list(
      #ct_alive = lm(ct_alive ~ ct + S, sim_fw_df),
      #richness = lm(richness ~ ct + S, sim_fw_df),
      #  max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_df),
      w_avg_tlvl = lm(w_avg_tlvl ~ richness + ct_alive, sim_fw_df),
      avg_omnivory = lm(avg_omnivory ~ w_avg_tlvl + ct_alive + richness, sim_fw_df),
      avg_int_strength = lm(avg_int_strength ~ w_avg_tlvl + ct_alive + richness + h, sim_fw_df),
      pop_stab = lm(pop_stab ~ Z + richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_df),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive, sim_fw_df),
      sae_even = lm(sae_even ~ richness, sim_fw_df),
      cpe_int = lm(cpe_int ~ richness + avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + h, sim_fw_df),
      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_df)
    )
    ),
  tar_target(sem, as.psem(sem_model_list)),
  tar_target(sem_coeff, {
    ti <- summary(sem)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti #%>%
      #filter(abs(Std.Estimate) > 0.1)# %>%
#  mutate(
#    Response = var_replacement()[Response],
#    Predictor = var_replacement()[Predictor]
#  ) %>%
    }),
  tar_target(tab_sem_coeff,
    sem_coeff %>%
      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
      collapse_rows(1, valign = "middle") %>%
      kable_styling()
    ),
  tar_target(sem_collinearity,
    map_dfr(setNames(sem_model_list, names(sem_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_rsquared,
    map_dfr(sem_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

@@

@@

```{targets p-stab-rich}
list(
#  tar_target(p_stab_s_prod,
#    sim_fw %>%
#      filter(productivity %in% c(5, 30), rho == 0, env_stoch == .3) %>%
#      ggplot(aes(x = richness, y = stab_com, color = as.factor(productivity))) +
#      geom_point() +
#      geom_smooth() +
#      labs(x = "Species richness", y = "Community stability", color = "Productivity") +
#      theme_bw()),
    tar_target(p_stab_s_env_stoch,
      sim_fw %>%
        filter(env_stoch %in% c(.5, 1.5), rho == 0, productivity == 5) %>%
        ggplot(aes(x = richness, y = stab_com, color = as.factor(env_stoch))) +
        geom_point() +
        geom_smooth() +
        labs(x = "Species richness", y = "Community stability", color = "Env. variability") +
        theme_bw()),
      tar_target(p_stab_s_resp_div,
        sim_fw %>%
          filter(rho %in% c(0, 1), productivity == 5, env_stoch == .5) %>%
          ggplot(aes(x = richness, y = stab_com, color = as.factor(1 - rho))) +
          geom_point() +
          geom_smooth() +
          labs(x = "Species richness", y = "Community stability", color = "Response diversity") +
          theme_bw()
      ),
      tar_target(p_stab_s_stress,
         plot_grid(
#           p_stab_s_prod,
           p_stab_s_env_stoch,
           p_stab_s_resp_div,
           labels = "auto"
         )
      )
)
```

@@

```{targets p-ct-rich-stab}
list(
  tar_target(p_ct_stab,
    sim_fw %>%
      filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
      pivot_longer(c(stab_com, async, sae_total, cpe,
          sae_even, evenness_sae,
          cpe_int, cpe_env, stab_pop
          ), names_to = "async_decomp", values_to = "values") %>%
      mutate(async_decomp = var_replacement()[async_decomp]) %>%
      ggplot(aes(x = ct_alive, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Connectance", y = "Asynchrony component") +
      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
      theme_bw()
    ),
  tar_target(p_rich_stab,
    sim_fw %>%
      filter(rho %in% c(0), productivity == 5, env_stoch == .5) %>%
      pivot_longer(c(stab_com, async, sae_total, cpe,
          sae_even, evenness_sae,
          cpe_int, cpe_env, stab_pop
          ), names_to = "async_decomp", values_to = "values") %>%
      mutate(async_decomp = var_replacement()[async_decomp]) %>%
      ggplot(aes(x = richness, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Species richness", y = "Asynchrony component") +
      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
      theme_bw()
    )
)
```

@@

@@

@@

summary(lm(cpe_env ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
summary(lm(cpe_int ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
summary(lm(cpe ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
performance::check_collinearity(lm(cpe_env ~ richness+ct_alive+avg_omnivory+rho, sim_fw))
mod_cpe <- lm(cpe ~ avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + productivity + rho, sim_fw)
summary(mod_cpe_int)
performance::check_collinearity(mod_cpe_int)

mod_cpe <- lm(log(cpe) ~ avg_int_strength + avg_omnivory + w_avg_tlvl + ct_alive + productivity + rho, sim_fw)

summary(mod_cpe)
plot(mod_cpe)
performance::check_collinearity(mod_cpe_int)

@@

```{r}
tar_load(sim_fw_cons)
sim_fw_cons %>%
  filter(env_stoch == .6, rho == 1, Z == 100, productivity == 5) %>%
  ggplot(aes(x = richness, y = stab_com, color = as.factor(h))) +
  geom_point() +
  geom_smooth()

sim_fw %>%
  filter(env_stoch == .6, rho == 0, Z == 100, productivity == 15) %>%
  ggplot(aes(x = richness, y = async, color = as.factor(h))) +
  geom_point() +
  geom_smooth()

sim_fw_cons %>%
  filter(env_stoch == .6, rho == 0, Z == 100, productivity == 30) %>%
  ggplot(aes(x = richness, y = pop_stab, color = as.factor(h))) +
  geom_point() +
  geom_smooth()
```

```{r}
plot(richness ~ Z, sim_fw)
```

@@

```{r}
tar_read(sem_coeff) %>%
  filter(abs(Std.Estimate) > .05)
tar_read(sem_rsquared)
tar_load(sem_collinearity)
sem_collinearity %>%
  print(., n = 38)
```

```{r}
tar_load(sem_model_list)
tar_load(sim_fw_df)
sem_boot <- bootEff(sem_model_list,
  R = 10, seed = 13, parallel = "no")

sem_eff <- semEff(sem_model_list, ci.type = "perc", R = 10, seed = 13, parallel = "no")
```

```{r}
mod_tot_scaled <- lm(stab_com ~
  richness + productivity + rho + env_stoch +
  ct_alive + avg_int_strength + avg_omnivory + w_avg_tlvl +
  richness : productivity +
  richness : rho +
  richness : env_stoch +
  richness : ct_alive +
  richness : avg_int_strength +
  richness : avg_omnivory +
  richness : w_avg_tlvl +
  richness : productivity : ct_alive +
  richness : productivity : w_avg_tlvl +
  richness : productivity : avg_int_strength +
  richness : productivity : avg_omnivory +
  richness : rho : ct_alive +
  richness : rho : w_avg_tlvl +
  richness : rho : avg_int_strength +
  richness : rho : avg_omnivory +
  richness : env_stoch : ct_alive +
  richness : env_stoch : w_avg_tlvl +
  richness : env_stoch : avg_int_strength +
  richness : env_stoch : avg_omnivory,
sim_fw %>%
  mutate(across(c("stab_com", "richness", "productivity", "rho", "env_stoch", "ct_alive", "avg_int_strength", "avg_omnivory", "w_avg_tlvl"), scale))

  )
summary(mod_tot)
predict(mod_tot)
summary(sim_fw$stab_com)
summary(sim_fw$avg_int_strength)
summary(sim_fw$w_avg_tlvl)
summary(sim_fw$avg_omnivory)

mod_tot <- lm(stab_com ~
  richness + productivity + rho + env_stoch +
  ct_alive + avg_int_strength + avg_omnivory + w_avg_tlvl +
  richness * productivity +
  richness * rho +
  richness * env_stoch +
  richness * ct_alive +
  richness * avg_int_strength +
  richness * avg_omnivory +
  richness * w_avg_tlvl +
  richness * productivity * ct_alive +
  richness * productivity * w_avg_tlvl +
  richness * productivity * avg_int_strength +
  richness * productivity * avg_omnivory +
  richness * rho * ct_alive +
  richness * rho * w_avg_tlvl +
  richness * rho * avg_int_strength +
  richness * rho * avg_omnivory +
  richness * env_stoch * ct_alive +
  richness * env_stoch * w_avg_tlvl +
  richness * env_stoch * avg_int_strength +
  richness * env_stoch * avg_omnivory,
mutate(sim_fw, across(c(stab_com, richness), log)) #, richness
  )
check_collinearity(lm(stab_com ~ richness + productivity + rho + env_stoch +
  ct_alive + avg_int_strength + avg_omnivory + w_avg_tlvl, sim_fw))
plot(mod_tot)

pred_data <- list(
  richness = log(seq(5, 30, 1)),
  ct_alive = c(.05, .10, .30),
  rho = c(0, .5, 1),
  avg_int_strength = c(.02, .04, .1),
  env_stoch = c(.2, .6),
  w_avg_tlvl = c(1.5, 1.7, 2),
  avg_omnivory = c(.01, .05, .1),
  productivity = c(5, 30),
  Z = 10
  ) %>% expand.grid()
pred_data$stab_com <- predict(mod_tot, newdata = pred_data)

@@

```{r}
p_pred_sr_ct_int <- pred_data %>%
  filter(
    productivity == 5,
    ct_alive %in% c(.1, .3),
    rho %in% c(0, 1),
    avg_int_strength %in% c(.02, .1),
    avg_omnivory == .05,
    w_avg_tlvl == 1.7) %>%
  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
  geom_line() +
  facet_grid(cols = vars(env_stoch), rows = vars(rho), labeller = label_both) +
  theme_bw()
ggsave(
  here("report", "figures", "p_pred_sr_ct_int.png"),
  plot = p_pred_sr_ct_int,
  scale = 2.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)
p_pred_sr_omn <- pred_data %>%
  filter(
    productivity == 5,
    ct_alive %in% c(.1),
    rho %in% c(0, 1),
    avg_int_strength %in% .02,
    avg_omnivory %in% c(.01, .1),
    w_avg_tlvl == 1.7) %>%
  ggplot(aes(x=richness, y = stab_com, color = as.factor(avg_omnivory))) +
  geom_line() +
  facet_grid(cols = vars(env_stoch), rows = vars(rho), labeller = label_both) +
  theme_bw()
ggsave(
  here("report", "figures", "p_pred_sr_omn.png"),
  plot = p_pred_sr_omn,
  scale = 2.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)

p_pred_sr_avg_tlvl <- pred_data %>%
  filter(
    productivity == 5,
    ct_alive %in% c(.1),
    rho %in% c(0, 1),
    avg_int_strength %in% .02,
    avg_omnivory %in% c(.05),
    w_avg_tlvl == c(1.5, 2)) %>%
  ggplot(aes(x=richness, y = stab_com, color = as.factor(w_avg_tlvl))) +
  geom_line() +
  facet_grid(cols = vars(env_stoch), rows = vars(rho), labeller = label_both) +
  theme_bw()
ggsave(
  here("report", "figures", "p_pred_sr_avg_tlvl.png"),
  plot = p_pred_sr_avg_tlvl,
  scale = 2.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)

pred_data %>%
  filter(
    rho == 0,
    ct_alive %in% c(.1, .3),
    avg_int_strength %in% c(.02, .1),
    avg_omnivory == .05,
    w_avg_tlvl == 1.7) %>%
  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
  geom_line() +
  facet_grid(cols = vars(env_stoch), rows = vars(productivity), labeller = label_both)

pred_data %>%
  filter(
    env_stoch == 0.2,
    ct_alive %in% c(.1, .3),
    rho %in% c(0, 1),
    avg_int_strength %in% c(.02, .1),
    avg_omnivory == .05,
    w_avg_tlvl == 1.7) %>%
  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
  geom_line() +
  facet_grid(cols = vars(rho), rows = vars(productivity), labeller = label_both) +
  theme_bw() +
  labs(
    x = "Species richness",
    y = "Community stability",
    linewidth = "Avg. Int",
    color = "Connectance"
  )
```

```{r}
pred_data %>%
  filter(
    env_stoch == 0.6,
    ct_alive %in% c(.1, .3),
    rho %in% c(0, 1),
    avg_int_strength %in% c(.02, .1),
    avg_omnivory == .05,
    w_avg_tlvl == 1.7) %>%
  ggplot(aes(x=richness, y = stab_com, color = as.factor(ct_alive), linewidth = as.factor(avg_int_strength))) +
  geom_line() +
  facet_grid(cols = vars(rho), rows = vars(productivity)) +
  theme_bw()
```

>>>>

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("tidyverse", "magrittr", "cowplot", "here", "arrow", "piecewiseSEM", "semEff", "easystats", "glmmTMB", "ggcorrplot", "kableExtra"))
source(here::here("R", "network_metrics.R"))
source(here::here("R", "string_replacements.R"))
source(here::here("R", "stability_decomposition.R"))
source(here::here("R", "model_helpers.R"))
source(here::here("R", "sem_helpers.R"))
```

@@

```{targets raw_sim}
list(
tar_target(sim_fw_file, here::here("data", "sim_fw"), format = "file"),
  tar_target(sim_fw, readRDS(sim_fw_file)),
  tar_target(sim_fw_df, as.data.frame(sim_fw)),
  tar_target(sim_fw_cons, readRDS(here::here("data", "sim_fw_cons"))),
  tar_target(sim_fw_cons_df, as.data.frame(sim_fw_cons))
  )
```

@@

```{targets sem-process}
list(
  tar_target(sim_fw_sem,
    sim_fw_df %>%
      mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae,
            sae_even, cpe_int, cpe_env), log))
    ),
  tar_target(sem_model_list,
    list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      #max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_sem),
      w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      avg_omnivory = lm(avg_omnivory ~ ct + S, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + h + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h + Z, sim_fw_sem),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
      sae_even = lm(sae_even ~ richness, sim_fw_sem),
      cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h + Z, sim_fw_sem),
      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_sem),
      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
    ),
  tar_target(sem, {
    ti <- as.psem(sem_model_list)
    update(ti, avg_omnivory %~~% w_avg_tlvl)
    }
    ),
  tar_target(sem_coeff, {
    ti <- summary(sem)$coefficients[, c(1, 2, 8, 9)]
    colnames(ti)[4] <- "Signif"
    ti #%>%
    #filter(abs(Std.Estimate) > 0.1)# %>%
    #  mutate(
    #    Response = var_replacement()[Response],
    #    Predictor = var_replacement()[Predictor]
    #  ) %>%
    }),
  tar_target(sim_eff_file, here::here("data", "sem_eff"), format = "file"),
  tar_target(sem_eff, {
    readRDS(sim_eff_file)
    #semEff(sem, ci.type = "perc", R = 10, seed = 13, parallel = "no", data = sim_fw_sem)
    }
    ),
  tar_target(sem_eff_tab, from_semEff_to_table(sem_eff)),
  tar_target(tab_sem_coeff,
    sem_coeff %>%
      kable(caption = "Standardized estimates for the Structural Equation Models.") %>%
      collapse_rows(1, valign = "middle") %>%
      kable_styling()
    ),
  tar_target(sem_collinearity,
    map_dfr(setNames(sem_model_list, names(sem_model_list)),
      performance::check_collinearity,
      .id = "response") %>%
    as_tibble),
  tar_target(sem_rsquared,
    map_dfr(sem_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
    ),
  tar_target(tab_sem_vif,
    sem_collinearity %>%
      mutate(
        response = var_replacement()[response],
        Term = var_replacement()[Term]
        ) %>%
      kable(
        caption = "Variance Inflation Factors for the Structural Equation Model.") %>%
      kable_styling()
    ),
  tar_target(tab_sem_rsquared,
    sem_rsquared %>%
      kable(caption = "Rsquared for the Structural Equation Model.") %>%
      kable_styling()
  )
)
```

@@

)
```

@@

```{targets p-stab-rich}
list(
#  tar_target(p_stab_s_prod,
#    sim_fw %>%
#      filter(productivity %in% c(5, 30), rho == 0, env_stoch == .3) %>%
#      ggplot(aes(x = richness, y = stab_com, color = as.factor(productivity))) +
#      geom_point() +
#      geom_smooth() +
#      labs(x = "Species richness", y = "Community stability", color = "Productivity") +
#      theme_bw()),
    tar_target(p_stab_s_env_stoch,
      sim_fw %>%
        filter(env_stoch %in% c(.5, 1.5), rho == 0) %>%
        ggplot(aes(x = richness, y = stab_com, color = as.factor(env_stoch))) +
        geom_point() +
        geom_smooth() +
        labs(x = "Species richness", y = "Community stability", color = "Env. variability") +
        theme_bw()),
      tar_target(p_stab_s_resp_div,
        sim_fw %>%
          filter(rho %in% c(0, 1), productivity == 5, env_stoch == .5) %>%
          ggplot(aes(x = richness, y = stab_com, color = as.factor(1 - rho))) +
          geom_point() +
          geom_smooth() +
          labs(x = "Species richness", y = "Community stability", color = "Response diversity") +
          theme_bw()
      ),
      tar_target(p_stab_s_stress,
         plot_grid(
#           p_stab_s_prod,
           p_stab_s_env_stoch,
           p_stab_s_resp_div,
           labels = "auto"
         )
      )
)
```

```{targets p_stab_rich_env_rho, tar_simple = TRUE}
sim_fw %>%
  filter(env_stoch %in% c(.1, .6), rho %in% c(0, .75), h == 3, Z == 100) %>%
  ggplot(aes(x = log(richness), y = log(stab_com), color = as.factor(rho))) +
  geom_point(alpha = .3) +
  geom_smooth(method = "lm") +
  facet_grid(cols = vars(env_stoch), labeller = label_both) +
  labs(
    x = "Species richness (Log)", y = "Community stability (Log)",
    color = "Environmental correlation"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")
```

@@

```{targets p-ct-rich-stab}
list(
  tar_target(p_ct_stab,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .1) %>%
      pivot_longer(c(stab_com, async, sae_total, cpe,
          sae_even, evenness_sae,
          cpe_int, cpe_env, stab_pop
          ), names_to = "async_decomp", values_to = "values") %>%
      mutate(async_decomp = var_replacement()[async_decomp]) %>%
      ggplot(aes(x = ct_alive, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Connectance", y = "Asynchrony component") +
      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
      theme_bw()
    ),
  tar_target(p_rich_stab,
    sim_fw %>%
      filter(rho %in% c(0), env_stoch == .1) %>%
      pivot_longer(c(stab_com, async, sae_total, cpe,
          sae_even, evenness_sae,
          cpe_int, cpe_env, stab_pop
          ), names_to = "async_decomp", values_to = "values") %>%
      mutate(async_decomp = var_replacement()[async_decomp]) %>%
      ggplot(aes(x = richness, y = values)) +
      geom_point() +
      geom_smooth() +
      labs(x = "Species richness", y = "Asynchrony component") +
      facet_wrap(~async_decomp, ncol = 3, scales = "free_y") +
      theme_bw()
    )
)
```

```{targets p_int_fw_str, tar_simple = TRUE}
p1 <- sim_fw %>%
  ggplot(aes(x = as.factor(richness), y = avg_int_strength)) +
  geom_point() +
  labs(x = "Species richness", y = "Avg. Interaction strength") +
  theme_bw()
p2 <- sim_fw %>%
  ggplot(aes(x = as.factor(Z), y = avg_int_strength)) +
  geom_boxplot() +
  labs(x = "PPBR", y = "Avg. Interaction strength") +
  theme_bw()
p3 <- sim_fw %>%
  filter(Z == 100) %>%
  ggplot(aes(x = as.factor(h), y = avg_int_strength)) +
  geom_boxplot() +
  labs(x = "Hill exponent", y = "Avg. Interaction strength") +
  theme_bw()
plot_grid(p1, p2, p3, ncol = 2)
```

@@

```{targets p_sem_tot_stab, tar_simple=TRUE}
tar_read(sem_eff_tab) %>%
  filter(effect_type == "total") %>%
  filter(response %in% c("async", "pop_stab", "stab_com")) %>%
  filter(!predictor %in% c("evenness_sae", "sae_even", "cpe_int", "cpe_env", "pop_stab", "async")) %>%
  mutate(across(c(response, predictor), ~var_replacement()[.x])) %>%
  ggplot(aes(
      x = predictor,
      y = effect,
      ymin = lower_ci,
      ymax = upper_ci)
    ) +
  geom_pointrange() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_grid(cols = vars(response)) +
  labs(x = "Predictor", y = "Total effect") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

@@

```{r}
tar_load(sim_fw_df)
sim_fw_df %<>%
  mutate(across(c(stab_com, pop_stab, async, cpe, sae_total, evenness_sae, sae_even, cpe_int, cpe_env), log))

tu <- list(
      #ct_alive = lm(ct_alive ~ ct + S, sim_fw_df),
      #richness = lm(richness ~ ct + S, sim_fw_df),
      #  max_tlvl = lm(max_tlvl ~ ct + S + Z, sim_fw_df),
      w_avg_tlvl = lm(w_avg_tlvl ~ richness + ct_alive + Z, sim_fw_df),
      avg_omnivory = lm(avg_omnivory ~ ct_alive + richness, sim_fw_df),
      avg_int_strength = lm(avg_int_strength ~ ct_alive + richness + h, sim_fw_df),
      pop_stab = lm(pop_stab ~ Z + richness + avg_int_strength + w_avg_tlvl + ct_alive + env_stoch + h, sim_fw_df),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + w_avg_tlvl + ct_alive, sim_fw_df),
      sae_even = lm(sae_even ~ richness, sim_fw_df),
      cpe_int = lm(cpe_int ~ richness + avg_int_strength + w_avg_tlvl + ct_alive + h, sim_fw_df),
      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_df),
      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_df),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_df)
    )
map_dfr(tu, check_collinearity)
sem <- as.psem(tu)
sem <- update(sem, avg_omnivory %~~% w_avg_tlvl)
```

```{r}
ti <- compute_rotated_pca(sim_fw_df %>% select(
    richness, w_avg_tlvl, avg_omnivory, avg_int_strength,
    max_tlvl
    ), naxis = 2)
p <- plot_rotated_pca(pca_rotated = ti, axis = c(1, 2))
p[[1]]
```

```{r}
ti <- compute_rotated_pca(sim_fw_df %>% select(
    w_avg_tlvl, avg_omnivory, avg_int_strength
    ), naxis = 2)
p <- plot_rotated_pca(pca_rotated = ti, axis = c(1, 2))
p[[1]]
p$rotated
cor(ti$rotated$scores[, "RC1"], sim_fw_df[,"richness"])
```

@@

@@

@@

```{r}
tar_read(sem_coeff) %>%
  filter(abs(Std.Estimate) > .1) %>%
  mutate(Std.Estimate = round(Std.Estimate, 1))
tar_read(sem_rsquared) %>%
  mutate(R.squared = round(R.squared, 2))
tar_load(sem_collinearity)
tar_read(sem_collinearity) %>%
  print(., n = 38)
```

```{r}
tar_load(c(sim_fw_sem, sim_fw))
mod_tot_scaled <- lm(stab_com ~
  richness + rho + env_stoch +
  ct_alive + avg_int_strength + w_avg_tlvl +
  richness : rho +
  richness : env_stoch +
  richness : ct_alive +
  richness : avg_int_strength +
  richness : w_avg_tlvl +
  richness : rho : ct_alive +
  richness : rho : w_avg_tlvl +
  richness : rho : avg_int_strength +
  richness : env_stoch : ct_alive +
  richness : env_stoch : w_avg_tlvl +
  richness : env_stoch : avg_int_strength,
sim_fw_sem %>%
  mutate(across(c("stab_com", "richness", "productivity", "rho", "env_stoch", "ct_alive", "avg_int_strength", "avg_omnivory", "w_avg_tlvl"), scale))

  )
summary(sim_fw$stab_com)
summary(sim_fw$avg_int_strength)
summary(sim_fw$w_avg_tlvl)
summary(sim_fw$avg_omnivory)

mod_tot <- lm(stab_com ~
  richness  + rho + env_stoch +
  ct_alive + w_avg_tlvl + Z +
  avg_int_strength +
  h +
  richness * rho +
  richness * env_stoch +
  richness * ct_alive +
  richness * avg_int_strength +
  richness * h +
  richness * w_avg_tlvl +
  richness * Z +
  richness * rho * ct_alive +
  richness * rho * w_avg_tlvl +
  richness * rho * avg_int_strength +
  richness * rho * h +
  richness * rho * Z +
  richness * env_stoch * ct_alive +
  richness * env_stoch * Z +
  richness * env_stoch * avg_int_strength+
  richness * env_stoch * h +
  richness * env_stoch * w_avg_tlvl,
  mutate(sim_fw, across(c(stab_com, richness), log)) #, richness
  )
check_collinearity(lm(stab_com ~ richness + rho +
    env_stoch + avg_int_strength +
  ct_alive + w_avg_tlvl + Z + h, sim_fw))
plot(mod_tot)

pred_data <- list(
  richness = log(seq(1, 30, 1)),
  ct_alive = c(.05, .10, .30),
  rho = c(0, .75, 1),
  avg_int_strength = c(.01, .02, .05, .1),
  env_stoch = c(.1, .3),
  w_avg_tlvl = c(1.5, 2, 3),
  Z = c(10, 100),
  h = c(2, 3)
  ) %>% expand.grid()
pred_data$stab_com <- predict(mod_tot, newdata = pred_data)
```

```{r}
p_pred_sr_int <- pred_data %>%
  filter(
    ct_alive %in% c(.1),
    rho %in% c(0, .75),
    Z == 10,
    h %in% c(3),
    avg_int_strength %in% c(.01, .05),
    w_avg_tlvl == 1.5
    ) %>%
  ggplot(aes(
      x = richness, y = stab_com,
      color = as.factor(rho),
      linetype = as.factor(avg_int_strength),
      )) +
  geom_line(linewidth = 2) +
  facet_grid(cols = vars(env_stoch), labeller = label_both) +
  labs(
    x = "Species richness (Log)", y = "Community stability (Log)",
    linetype = "Avg. Interaction strength",
    color = "Environmental correlation"
  ) +
  theme_bw() +
  theme(legend.position = "bottom")
ggsave(
  here("report", "figures", "p_pred_sr_int.png"),
  plot = p_pred_sr_int,
  scale = 2.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)
```

```{r}
plot_grid(
  tar_read(p_stab_rich_env_rho) + theme(legend.position = "none"),
  p_pred_sr_int)
```

```{r}

p_pred_sr_avg_tlvl_h <- pred_data %>%
  filter(
    ct_alive %in% c(.3),
    h %in% c(2,3),
    rho %in% c(0, 1),
    Z == 10,
    avg_int_strength %in% c(.1),
    w_avg_tlvl == c(1.5, 3)) %>%
  ggplot(aes(x = richness, y = stab_com, linewidth = as.factor(w_avg_tlvl), color = as.factor(h))) +
  geom_line() +
  facet_grid(cols = vars(env_stoch), rows = vars(rho), labeller = label_both) +
  theme_bw()
ggsave(
  here("report", "figures", "p_pred_sr_avg_tlvl_h.png"),
  plot = p_pred_sr_avg_tlvl,
  scale = 2.4,
  width = 88,
  height = 88 * 1,
  units = "mm"
)
```

```{r}
```

```{r}
tar_load(sem_eff_tab)
sem_eff_tab %>%
  filter(abs(effect) > .1) %>%
  filter(effect_type == "direct") %>%
  print(., n = 30)

@@

```{r}
tar_load(sim_fw_sem)
sim_fw_sem %<>% mutate(richness = sqrt(richness))
ti <- as.psem(sem_model_list)
update(ti, avg_omnivory %~~% w_avg_tlvl)
sem_coeff <- summary(ti)$coefficients[, c(1, 2, 8, 9)]
map_dfr(sem_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
```

```{r}
sem_model_list <- list(
      ct_alive = lm(ct_alive ~ ct + S, sim_fw_sem),
      richness = lm(richness ~ ct + S, sim_fw_sem),
      #max_tlvl = lm(max_tlvl ~ ct + S, sim_fw_sem),
      #w_avg_tlvl = lm(w_avg_tlvl ~ ct + S + Z, sim_fw_sem),
      #avg_omnivory = lm(avg_omnivory ~ ct + S, sim_fw_sem),
      avg_int_strength = lm(avg_int_strength ~ ct + S + h + Z, sim_fw_sem),
      pop_stab = lm(pop_stab ~ richness + avg_int_strength + ct_alive + env_stoch, sim_fw_sem),
      evenness_sae = lm(evenness_sae ~ richness + avg_int_strength + ct_alive, sim_fw_sem),
      sae_even = lm(sae_even ~ richness, sim_fw_sem),
      cpe_int = lm(cpe_int ~ richness + avg_int_strength + ct_alive, sim_fw_sem),
      cpe_env = lm(cpe_env ~ richness + rho, sim_fw_sem),
      async = lm(async ~ sae_even + evenness_sae + cpe_env + cpe_int, sim_fw_sem),
      stab_com = lm(stab_com ~ pop_stab + async, sim_fw_sem)
    )
ti <- as.psem(sem_model_list)
update(ti, avg_omnivory %~~% w_avg_tlvl)
sem_coeff <- summary(ti)$coefficients[, c(1, 2, 8, 9)]
map_dfr(sem_model_list, rsquared) %>%
      mutate(Response = var_replacement()[Response]) %>%
      select(Response, R.squared)
```
